Language-Based Security for Low-Level MPC

### 2024-06-25 revision-2/minitypes.tex
checkpoint

\newcommand{\tj}[5]{#1,#2 \vdash_{#3} #4 : #5}
\newcommand{\cty}[2]{c(#1,#2)}
\newcommand{\setit}[1]{\{ #1 \}}
\newcommand{\ty}{T}

@@

  \inferrule[PubM]
  {}
  {\tj{\Gamma}{\varnothing}{\cid}{\rvl{w}}{\setit{\rvl{w}}}}

@@

  \inferrule[Share]
  {\tj{\Gamma}{R}{\cid}{\be}{\ty} \\ \oplus \in \{ \fplus,\fminus,\ftimes \}}
  {\tj{\Gamma}{R;\rx{w}{\cid}}{\cid}{\flip{w} \oplus \be}{\setit{\cty{\rx{w}{\cid}}{\ty}}}}

@@

\begin{theorem}
  Given $\varnothing,R \vdash \prog : \Gamma$ and:
  $$\seclab(\bigcup_{\mx{w}{\cid} \in X} \Gamma(\mx{w}{\cid}) \cup \flips(\prog)_C) = \lolab$$
  for $X \defeq \dom(\Gamma)_C$.
  Then $\prog$ satisfies gradual release.
\end{theorem}

$$
\mx{x}{1} : \setit{\rx{x}{1}}

\mx{x}{2} : \setit{\cty{\rx{x}{1}}{\sx{x}{1}}}
$$

$$
\mx{c}{1} : \setit{\rx{c}{1}}

\mx{c}{2} : \setit{ \cty{\rx{c}{1}}{\setit{\rx{a}{1},\rx{a}{2},\rx{b}{1},\rx{b}{2}}} }
$$

>>>>

\newcommand{\tj}[5]{#1,#2 \vdash_{#3} #4 : #5}
\newcommand{\cty}[2]{c(#1,#2)}
\newcommand{\setit}[1]{\{ #1 \}}
\newcommand{\ty}{T}
\newcommand{\eqs}{C}
\newcommand{\toeq}[1]{\lfloor #1 \rfloor}
\newcommand{\autheq}[1]{\phi_{\mathrm{auth}}(#1)}
\newcommand{\upgrade}[1]{\uparrow #1}

@@

@@

  \inferrule[PubM]
  {}
  {\tj{\Gamma}{\varnothing}{\cid}{\rvl{w}}{\Gamma(\rvl{w})}}

  \inferrule[Share]
  {\tj{\Gamma}{R}{\cid}{\be}{\ty} \\ \oplus \in \{ \fplus,\fminus \}}
  {\tj{\Gamma}{R;\rx{w}{\cid}}{\cid}{\be \oplus \flip{w}}{\setit{\cty{\rx{w}{\cid}}{\ty}}}}

@@

Then a main result is that protocols where the collective messages received by the
adversary are low security satisfy gradual release.
\begin{theorem}[Confidentiality Type Safety]
  Given $\Gamma_1,R \vdash \prog : \Gamma_2$ where $\Gamma_1$ is sound for
  preprocessing and:
  $$\seclab(\bigcup_{\mx{w}{\cid} \in X} \Gamma_2(\mx{w}{\cid}) \cup \flips(\prog)_C) = \lolab$$
  for $X \defeq \dom(\Gamma_2)_C$.
  Then $\prog$ satisfies gradual release.
\end{theorem}

This definition accounts for preprocessing of memories. In the default
case where initial memories just contain secrets and the random tape,
we can take $\Gamma_1$ to be $\varnothing$ In cases of nontrivial
pre-processing we need to define $\Gamma_1$ \cnote{and also a formal
  notion of soundness}. For example, in a 2-client Beaver Triple
scheme, we imagine that client 1's secret $x$ is shared as
messages $\mx{x}{1}$ and $\mx{x}{x}$ in the initial memory, obtained
via the ``0-time-pad'' use of the random value $\rx{x}{1}$.
So in this case $\Gamma_1$ would contain:
\begin{mathpar}
\mx{x}{1} : \setit{\rx{x}{1}}

\mx{x}{2} : \setit{\cty{\rx{x}{1}}{\setit{\sx{x}{1}}}}
\end{mathpar}
Similarly, we imagine that clients 1 and 2 possess respective
shares of random values $a$ and $b$ on their random tape:
$$
\rx{a}{1}\quad  \rx{a}{2}\quad \rx{b}{1}\quad \rx{b}{2} 
$$
as well as shares $\mx{c}{1}$ and $\mx{c}{2}$ of a value
$c \defeq a * b$, i.e.:
$$c \defeq
(\rx{a}{1} \fplus \rx{a}{2}) \ftimes (\rx{b}{1} \fplus \rx{b}{2})$$
so $\Gamma_1$ contains:
\begin{mathpar}
  \mx{c}{1} : \setit{\rx{c}{1}}

\mx{c}{2} : \setit{ \cty{\rx{c}{1}}{\setit{\rx{a}{1},\rx{a}{2},\rx{b}{1},\rx{b}{2}}} }
\end{mathpar}

\section{Confidentiality and Integrity Types for $\minifed$}

\begin{mathpar}
  \inferrule[Value] {}
            {\tj{\Gamma}{\varnothing}{\cid}{v}{\varnothing}}

  \inferrule[PubM]
  {}
  {\tj{\Gamma}{\varnothing}{\cid}{\rvl{w}}{\Gamma(\rvl{w})}}

  \inferrule[Share]
  {\tj{\Gamma}{R}{\cid}{\be}{\ty} \\ \oplus \in \{ \fplus,\fminus \}}
  {\tj{\Gamma}{R;\rx{w}{\cid}}{\cid}{\be \oplus \flip{w}}{\setit{\cty{\rx{w}{\cid}}{\ty}}}}

  \inferrule[Command]
  {\tj{\Gamma}{R_1}{\cid}{\be}{\ty} \\ \Gamma; x : \ty,R_2, \eqs \cup \{ x = \toeq{\elab{\be}{\cid}} \} \vdash \prog : \Gamma'}
  {\Gamma,R_1;R_2, \eqs \vdash x := \elab{\be}{\cid};\prog : \Gamma'}

  \inferrule[Assert]
  {\eqs \vdash \toeq{\elab{\be_1}{\cid}} = \toeq{\elab{\be_2}{\cid}} 
              \\ \Gamma; R, \eqs \vdash \prog : \Gamma'}
  {\Gamma,R,\eqs \vdash \elab{\assert{\be_1 = \be_2}}{\cid};\prog : \Gamma'}

  \inferrule[Auth]
  {\eqs \vdash \toeq{\autheq{\mesg{w}}}
              \\ \Gamma; \elab{\mesg{w}}{\cid} : \upgrade{\Gamma(\elab{\mesg{w}}{\cid})}, R, \eqs \vdash \prog : \Gamma'}
  {\Gamma,R,\eqs \vdash \elab{\assert{\autheq{\mesg{w}}}}{\cid};\prog : \Gamma'}

  \inferrule[Term]
  {}
  {\Gamma,\varnothing \vdash \varnothing: \Gamma,\varnothing}          
\end{mathpar}
